Statistical performance analysis of neural mass models?

### 2013-04-11 manuscript/manuscript.tex
add relation to general model to J and R

Present 3 models?

>>>>

The model focused on in the following
estimation sections is the formulation by Jansen and Rit \cite{Jansen-Rit-95}.
Given space limitations we refer the reader to the article by Jansen
and Rit\cite{Jansen-Rit-95} where the original state-space equations
are presented. The parameters that were described in this section are related to the Jansen and Rit paper by
\begin{align}
    A =& \frac{\alpha_{pe}}{2e_0c_1} = \frac{\alpha_{pi}}{2e_0c_3} = \frac{\alpha_{ep}}{2e_0c_2} = \frac{\alpha_{xp}}{2e_0} \\
    B =& \frac{\alpha_{ip}}{2e_0c_4} \\
    a =& \frac{1}{\tau_{pe}} = \frac{1}{\tau_{pi}} = \frac{1}{\tau_{ep}} = \frac{1}{\tau_{xp}} \\
    b =& \frac{1}{\tau_{ip}},
\end{align}
where $e_0$ is a parameter that scales the maximum firing rate, $A$ and $B$ are synaptic gains for excitation and inhibition respectively, and $a$ and $b$ are the reciprocals of the synaptic time constants for excitation and inhibition, respectively, and the subscripts $p$, $e$, $x$, and $i$ denote pyramidal ($p$), excitatory interneuron (spiny stellate) ($e$), external ($x$) or inhibitory interneuron ($i$) populations, respectively. By making the assumption that all excitatory synapses share the same time constants and by defining the connectivity constants, $c_1$, $c_2$, $c_3$ and $c_4$, the network of neural masses on the left side of Figure~\ref{fig:JansenAndRit} can be reduced to the system depicted on the right hand side.
Present 3 models?
